---
drake_cache: ".UI"
---

## Setup environment

  * Addins: Initiate drake -> `drake$source_plan()` -> `drake$makePlan()`.
  
  * `web$browse()` to see the output. 
  
  * If any change to Rmd, save the Rmd, then `drake$update()` -> `web$browser()` to see the change.
  
  * Your html output file is in `web$output_filepath()`.

```{r makecondition}
library(dplyr)
library(htmltools)
library(econR)
.GlobalEnv$web <- econR::Web()
web$foldername="docs" # output folder name
web$html_filename <- "index.html"
xfun::download_file(drake::file_in("https://www.dropbox.com/s/s4mv5ebhsqanpew/heritage.Rdata?dl=1"), mode="wb")
load("~/Github/109-2-app101/UI/widget_heritage.Rda", envir = .GlobalEnv)
load("~/Github/109-2-app101/UI/heritage.Rdata", envir = .GlobalEnv)
heritageData %>%
  filter(
    abs(longitude-121) <= 2.5,
    abs(latitude-24) <= 2.5
  ) -> heritageData
```

### side nav

```{r navbarContent}
navbarContent <- tags$nav(
  tags$div(class="container valign-wrapper",
           tags$h5("臺灣古蹟")))
```

```{r googleSearch}
searchContent <- URLencode(heritageData$caseName[[1]])
googleSearch <- glue::glue('https://www.google.com/search?q={searchContent}&sxsrf=ALeKk01D05Oz12ZZcjb7vxeL2fV7sKa_mg:1617153946605&source=lnms&tbm=isch&sa=X&ved=2ahUKEwi6_6L0r9nvAhXIyYsBHcHzCQ4Q_AUoAnoECAEQBA&biw=1920&bih=981')
googleSearch
```



```{r slide_out}
slide_out <- tags$ul(id="slide-out", class="sidenav", style="z-index: 9999;",
    tags$li( tags$div(class="user-view", 
      tags$div(class="background", 
        tags$img(src=heritageData$representImage[[1]])
      ),
      tags$a(href="#user", tags$img(class="circle image-icon", src=heritageData$representImage[[1]])),
      tags$a(href=googleSearch, target="_blank", #"#name", 
             tags$span(class="white-text name",heritageData$caseName[[1]],
             tags$i(class="material-icons red darken-2"," photo")))
      )
    ),
    tags$li(
      tags$div(
        class="container",
        heritageData$pastHistory[[1]])
      #tags$a(href="#!", tags$i(class="material-icons"," info_outline"), 
      #              tags$p(heritageData$pastHistory[[1]]))
      )
  )
```


```{r slide_out_dataTarget}
slide_out_dataTarget <- tags$a(href="#", `data-target`="slide-out", class="sidenav-trigger",
                               tags$div(style="margin: 5px",
                                 tags$i(class="material-icons"," info_outline"))
)
```


```{r sideNav}
sideNav <- tagList(
  navbarContent,
  slide_out,
  slide_out_dataTarget
)
```


### Widgets

  * Widgets can be designed in a separate file and saved in a Rdata for loading here.
  
  * While loading, make sure `envir = .GlobalEnv`.
  
  * Label widget loading chunk `makecondition_xxx`. 
  
```{r makecondition_widgets}
.root <- rprojroot::is_rstudio_project$make_fix_file()
# load(file.path(.root(),"widget_heritage.Rda"), envir = .GlobalEnv)
library(leaflet)
```

```{r widget_heritage}
leaflet() %>% addTiles() %>%
  addMarkers(data = heritageData, lng=~longitude, lat=~latitude, popup = ~caseName,
             clusterOptions = markerClusterOptions())
```

```{r save_widgetHeritage}
save_html(
  widget_heritage, file=file.path(dirname(web$output_filepath()),"widget_heritage.html")
)
```

### Floating action

```{r floatActionBtns}
floatActionBtns <- tags$div(class="fixed-action-btn", 
  tags$a(class="btn-floating btn-large red", 
    tags$i(class="large material-icons", "mode_edit")
  ),
  tags$ul( 
    tags$li( tags$a(class="btn-floating red", tags$i(class="material-icons", "insert_chart"))),
    tags$li( tags$a(class="btn-floating yellow darken-1", tags$i(class="material-icons", "format_quote"))),
    tags$li( tags$a(class="btn-floating green", tags$i(class="material-icons"," publish"))),
    tags$li( tags$a(class="btn-floating blue", tags$i(class="material-icons", "attach_file")))
  )
)
      
```

### Body Tags

```{r iframe_widgetHeritage}
iframe_widgetHeritage <- tags$div(class="video-container",
                                  tags$iframe(
                                         src="widget_heritage.html",
                                         height="100%", #widget_heritage$sizingPolicy$defaultHeight,
                                         weight="400", #widget_heritage$sizingPolicy$defaultWidth,
                                          frameborder="0", allowfullscreen=NA
                                       )
)
```


```{r bodyTags}
bodyTags <- {
  htmltools::tagList(
    sideNav,
    tags$div(class="container",
             tags$div(class="row",
                      tags$div(class="col s12 ",
                               widget_heritage
                               )
                      ),
             floatActionBtns)
  )
}
```


## HTML Structure

```{r html_placeholder}
html_placeholder <- tags$html(
  tags$head(
    do.call(htmltools::tagList, headTags),
    tags$meta(
      name="viewport",
      content="width=device-width, initial-scale=1.0"
    )
  ),
  tags$body(
    do.call(htmltools::tagList, bodyTags)
  )
)
```

## Dependencies

### Head Tags

```{r headTags}
headTags <- {
  htmltools::tagList(
    htmltools::tags$link(
      href="https://fonts.googleapis.com/icon?family=Material+Icons",
      rel="stylesheet"
    )
  )
}
```

### Define dependency

```{r myDependency}
myDependency <- htmltools::htmlDependency(
  name="myown",
  version="1.0",
  src=c(filepath=web$cssJsPath),
  stylesheet = "css/mystyle.css",
  script = "js/mydesign.js",
  head = '<link rel="stylesheet" href="https://fonts.googleapis.com/css?family=Noto+Sans+TC">
'
)
```

  * If src is in other path, use `web$config_cssJsPath("your_path")` in **makecondition** -- no need to change `web$cssJsPath` (it will change accordingly).


```{r local_jquery, drake=F}
local_jquery <- 
  htmltools::htmlDependency(
    name="jquery",
    version="3.5.1",
    src=c(href = "lib/jquery-3.5.1"),
    # to use the same library here must use href, not filepath; otherwise, the current jquery system will be removed.
    script = c("jquery.min.js")
  )
```

### Attach dependency


```{r html_complete}
html_complete <- 
  htmltools::tagList(
    html_placeholder,
    web$htmlDependencies$materialise(),
    web$htmlDependencies$jquery(),# local_jquery, 
    myDependency
  )
```

  * If not using jquery from htmlwidgets, replace `local_jquery` with `web$htmlDependencies$jquery()`


## Save

```{r save_html}
htmltools::save_html(
  html_complete, 
  file = web$output_filepath(),
  libdir="lib"
)
```

## Browse

```{r}
web$browse()
```



