---
title: "chinese_enumerates"
author: "frank"
date: "2021年5月1日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
chineseNumber1 <- "零一二三四五六七八九十"
chineseNumber2 <- "零壹貳參肆伍陸柒捌玖拾"
chineseNumber1_char <- unlist(stringr::str_split(chineseNumber1,""))
chineseNumber2_char <- unlist(stringr::str_split(chineseNumber2,""))
```

It would be nice that you can process the following 
```{r}
fct_numbers <- factor(c("一","五","七", "參拾參","五十七","拾壹"))
oldLevels <- levels(fct_numbers)
oldLevels
```
so that its level sequence will be 
```{r}
c("一","五","七","拾壹", "參拾參","五十七")
```
without using
```{r}
levels(fct_numbers) <- c("一","五","七","拾壹", "參拾參","五十七") # OR
fct_numbers <- factor(c("一","五","七", "參拾參","五十七","拾壹"), 
                      levels = c("一","五","七","拾壹", "參拾參","五十七")
)
```

In other words, your algorithm should take these three symbols:

  * `chineseNumber1_char`, `chineseNumber1_char`, `oldLevels`
  

and come out 

  * `newLevels`

which is a character with correct order. (Imagine that oldLevels can be any randomly given string of chinese number characters.)

For simplicity, we assume that `oldLevels` elements are between 0 and 99 in Chinese characters.

  
```{r}
chineseNumber1 <- "零一二三四五六七八九十"
chineseNumber2 <- "零壹貳參肆伍陸柒捌玖拾"
chineseNumber1_char <- unlist(stringr::str_split(chineseNumber1,""))
chineseNumber2_char <- unlist(stringr::str_split(chineseNumber2,""))
oldLevels <- c("一", "七", "五", "五十七", "參拾參", "拾壹")
oldLevels <- c("玖","三十柒","玖拾二","參拾三","五十七","五","拾壹","十捌","陸十")
library(stringr)
library(glue)
library(purrr)
{   
    pattern1 <-glue::glue("(?<=[十拾])[",chineseNumber1_2_char,"]")
    pattern2 <-glue::glue("[",chineseNumber1_2_char,"](?=[十拾])")
    pattern3 <-glue::glue("(?<=)[十拾]")
    chineseNumber1_2_char <- paste0(chineseNumber1,chineseNumber2)
    is.integer0 <- function(x){
       return(is.integer(x) && length(x)==0)
    }
    map(
         seq_along(oldLevels),
         ~{
            if(str_detect(oldLevels[.x],pattern=pattern1) || str_detect(oldLevels[.x],pattern=pattern2)){
                  sum = 0
                  if(str_detect(oldLevels[.x],pattern3)){
                     sum = sum+10
                  }
                  if(str_detect(oldLevels[.x],pattern=pattern1)){
                      if(is.integer0(str_which(str_extract(oldLevels[.x],pattern=pattern1),chineseNumber1_char)))
                      {
                          sum = sum+str_which(str_extract(oldLevels[.x],pattern=pattern1),chineseNumber2_char)
                      }else{
                          sum = sum+str_which(str_extract(oldLevels[.x],pattern=pattern1),chineseNumber1_char)
                      } 
                  }
                  if(str_detect(oldLevels[.x],pattern=pattern2)){
                      if(is.integer0(str_which(str_extract(oldLevels[.x],pattern=pattern2),chineseNumber1_char)))
                      {
                          sum = sum+10*str_which(str_extract(oldLevels[.x],pattern=pattern2),chineseNumber2_char)
                      }else{
                          sum = sum+10*str_which(str_extract(oldLevels[.x],pattern=pattern2),chineseNumber1_char)
                      } 
                  }
            }else{
                 if(is.integer0(str_which(oldLevels[.x],chineseNumber1_char)))
                 {
                         sum = str_which(oldLevels[.x],chineseNumber2_char)
                 }else{
                         sum = str_which(oldLevels[.x],chineseNumber1_char)
                 } 
            }
            sum
         }
     )  -> oldlevel_to_number
    unlist(oldlevel_to_number) -> oldlevel_to_number
    names(oldlevel_to_number) <- oldLevels
    names(sort(oldlevel_to_number))
} -> newLevels
newLevels 
```
