---
title: "select_heritage"
author: "frank"
date: "2021年5月19日"
output: html_document
---

```{r}
xfun::download_file("https://www.dropbox.com/s/vt10xxig64levmj/list_heritageYears.json?dl=1", mode="wb")
list_heritageYears <- jsonlite::fromJSON("list_heritageYears.json")
```

## 引入chinese模組

```{r}
.root <- rprojroot::is_rstudio_project$make_fix_file()
source(
  file.path(.root(),"R/chinese_martin.R")
)
```

## 轉換data

```{r}
purrr::map(
  list_heritageYears,
  ~{
    chinese$convert2westernYears(.x)
  }
) -> list_heritageYears_converted
```


## 目標

```{r}
#' 找出時間點或時間區間有交集的古蹟
#'
#' @param list_heritageYears_converted a list of strings.
#' @param start a character of starting year
#' @param end a character of ending year. if NA, means until now
#'
#' @return integers showing the indices of heritage that fit the criterion
#' @export
#'
#' @examples
source("/Users/frankchao/Desktop/109-2-app101/weekly_progress/frank/time_interval.R")
library(lubridate)
library(dplyr)
filter_heritage <- function(list_heritageYears_converted, start, end=NA){
      create_interval(start,end) -> .interval
      find_ListObject_within_interval(list_heritageYears_converted,.interval) -> index_fits
      return(index_fits)
}
filter_heritage(list_heritageYears_converted, 1938, NA) -> from_1938_to_now
filter_heritage(list_heritageYears_converted, 1638, 1837 ) -> from_1638_to_1837
```


```{r}
#' 列出自何時以後存在的古蹟index
#'
#' @param list_heritageYears_converted 
#' @param since an integer of year
#'
#' @return
#' @export
#'
#' @examples
exist_since <- function(list_heritageYears_converted, since){
      create_interval(since,"2021") -> .interval
      find_ListObject_within_interval(list_heritageYears_converted,.interval) -> index_fits
      return(index_fits)
}
exist_since(list_heritageYears_converted,1980) -> since_1980
#' 列出在何時之前就存在的古蹟index
#'
#' @param list_heritageYears_converted 
#' @param before an integer of year
#'
#' @return
#' @export
#'
#' @examples
exist_before <- function(list_heritageYears_converted, before){
      create_interval("0001",before) -> .interval
      find_ListObject_within_interval(list_heritageYears_converted,.interval) -> index_fits
      return(index_fits)
}
exist_before(list_heritageYears_converted,1555) -> before_1555
```

# example

```{r}
c("1980","2000","1792","1683") -> year_test1
create_interval(year_test1,year_test1) -> interv1 
int_overlaps(interv1,interval(ymd("1970:01:01"),ymd("2001:01:01")))
c("1980") -> year_test2
create_interval(year_test2,year_test2)
create_interval("1980",NA)
create_interval("1895-1945","1895-1945")
create_interval(c("1895-1945","1872","1785"),c("1895-1945","1872","1785"))
create_interval(c("1895-1945","1872","一百一十"),c("1895-1945","1872","一百一十")) -> interv2
int_overlaps(interv2,interval(ymd("1930:01:01"),ymd("1941:01:01")))
```

# check
```{r}
# check filter_heritage
sample(which(from_1938_to_now),5) -> test1
list_heritageYears_converted[test1]
sample(which(from_1638_to_1837),5) -> test2
list_heritageYears_converted[test2]
# check exist_since
sample(which(since_1980),5) -> test
list_heritageYears_converted[test]
# check exist_before
sample(which(before_1555),5) -> test
list_heritageYears_converted[test]
```

# psuedo code

filter_heritage(data:list,start_year:charater,end_year:character)
1      time_interval1 = create_time_interval(start_year,end_year)
2      index_list = []
3      for atomic vector in data : 
4          interval_list = []
5          for all years in atomic vector:
6              if year == "1895-1945":
7                   convert it to time_interval(1895-01-01,1945-01-01) and store to 
8                   interval_list
9              elseif year is character(number) :
10                  convert it to time_interval(year-01-01,year-01-01) and store to 
11                  interval_list
12             else:
13                  jump
14         if there's any time overlap between elements of interval_list and time_interval1:
15             store index(atomic vector) to index_list
16      return index_list       







