---
drake_cache: ".myHtml"
---

## Setup environment

  * Addins: Initiate drake -> `drake$source_plan()` -> `drake$makePlan()`.
  
  * `web$browse()` to see the output. 
  
  * If any change to Rmd, save the Rmd, then `drake$update()` -> `web$browser()` to see the change.
  
  * You html output are in `web$output_filepath()`.

```{r makecondition}
library(dplyr)
library(htmltools)
library(econR)
.GlobalEnv$web <- econR::Web()
web$foldername="docs2" # output folder name
web$html_filename <- "index.html"

# Demo: htmlwidget embed
if(!file.exists("plt_gg_bikeRouteStm.Rda")) xfun::download_file("https://www.dropbox.com/s/ify9h26c172t7t5/plt_gg_bikeRouteStm.Rda?dl=1", mode="wb")
load("plt_gg_bikeRouteStm.Rda", envir = .GlobalEnv)

```

### Widgets


```{r save_widget}
save_widget = {
  plotly::partial_bundle(plt_gg_bikeRouteStm) %>%
    htmlwidgets::saveWidget(
    file=
      file.path(dirname(web$output_filepath()), "plt_gg_bikeRouteStm.html"),
    selfcontained = FALSE,
    libdir="lib"
  )
}
```

```{r iframe_widget}
iframe_widget <- {
  htmltools::tags$iframe(
    width="853", height="480",
    src = "plt_gg_bikeRouteStm.html",
    scrolling = "no",
    seamless = "seamless",
    frameBorder = "0"
  )
}
```

### Body Tags

```{r bodyTags}
bodyTags <- {
  htmltools::tagList(
    tags$main(
      tags$h5(class="center-align",
      "〖Title〗")
    ),
    tags$div(class="container",
             tags$div(class="row",
                      tags$div(class="col s3",
                        tags$h5(class="center-align", "〖sidebar panel〗")),
                      tags$div(class="col s9",
                               tags$div(class="video-container",
                                        iframe_widget))
                      ))
  )
}
```

  * `video-container` ensure the responsiveness of iframe embed.

## HTML Structure

```{r html_placeholder}
html_placeholder <- tags$html(
  tags$head(
    do.call(htmltools::tagList, headTags),
    tags$meta(
      name="viewport",
      content="width=device-width, initial-scale=1.0"
    )
  ),
  tags$body(
    do.call(htmltools::tagList, bodyTags)
  )
)
```

## Dependencies

### Head Tags

```{r headTags}
headTags <- {
  htmltools::tagList(
    htmltools::tags$link(
      href="https://fonts.googleapis.com/icon?family=Material+Icons",
      rel="stylesheet"
    )
  )
}
```

### Define dependency

```{r myDependency}
myDependency <- htmltools::htmlDependency(
  name="myown",
  version="1.0",
  src=c(filepath=web$cssJsPath),
  stylesheet = "css/mystyle.css",
  script = "js/mydesign.js",
  head = '<link rel="stylesheet" href="https://fonts.googleapis.com/css?family=Noto+Sans+TC">
'
)
```

  * If src is in other path, use `web$config_cssJsPath("your_path")` in **makecondition** -- no need to change `web$cssJsPath` (it will change accordingly).


```{r local_jquery}
local_jquery <- 
  htmltools::htmlDependency(
    name="jquery",
    version="3.5.1",
    src=c(href = "lib/jquery-3.5.1"),
    # to use the same library here must use href, not filepath; otherwise, the current jquery system will be removed.
    script = c("jquery.min.js")
  )
```

### Attach dependency


```{r html_complete}
html_complete <- 
  htmltools::tagList(
    html_placeholder,
    web$htmlDependencies$materialise(),
    local_jquery, 
    myDependency
  )
```

  * If not using jquery from htmlwidgets, replace `local_jquery` with `web$htmlDependencies$jquery()`


## Save

```{r save_html}
htmltools::save_html(
  html_complete, 
  file = web$output_filepath(),
  libdir="lib"
)
```

## Browse

```{r}
web$browse()
```



