---
title: "rank chinese number"
output: html_document
---

It is common to rank chinese number 一～十，壹～拾

```{r}
chineseNumber1 <- "零一二三四五六七八九十"
chineseNumber2 <- "零壹貳參肆伍陸柒捌玖拾"
chineseNumber1_char <- unlist(stringr::str_split(chineseNumber1,""))
chineseNumber2_char <- unlist(stringr::str_split(chineseNumber2,""))
```

It would be nice that you can process the following 
```{r}
fct_numbers <- factor(c("一","五","七", "參拾參","五十七","拾壹"))
oldLevels <- levels(fct_numbers)
oldLevels
```
so that its level sequence will be 
```{r}
c("一","五","七","拾壹", "參拾參","五十七")
```
without using
```{r}
levels(fct_numbers) <- c("一","五","七","拾壹", "參拾參","五十七") # OR
fct_numbers <- factor(c("一","五","七", "參拾參","五十七","拾壹"), 
                      levels = c("一","五","七","拾壹", "參拾參","五十七")
)
```

In other words, your algorithm should take these three symbols:

  * `chineseNumber1_char`, `chineseNumber1_char`, `oldLevels`
  

and come out 

  * `newLevels`

which is a character with correct order. (Imagine that oldLevels can be any randomly given string of chinese number characters.)

For simplicity, we assume that `oldLevels` elements are between 0 and 99 in Chinese characters.

  
```{r}
chineseNumber1 <- "零一二三四五六七八九十"
chineseNumber2 <- "零壹貳參肆伍陸柒捌玖拾"
chineseNumber1_char <- unlist(stringr::str_split(chineseNumber1,""))
chineseNumber2_char <- unlist(stringr::str_split(chineseNumber2,""))
oldLevels <- c("一", "七", "五", "五十七", "參拾參", "拾壹")

oldLevels_inArabicNumber <- { # Your algorithm
  mapChinese2 <- mapChinese1 <- as.character(0:10)
  names(mapChinese1) <- chineseNumber1_char
  names(mapChinese2) <- chineseNumber2_char
  
  stringr::str_replace_all(
    oldLevels, mapChinese1
  ) -> oldLevelsReplacement1
  stringr::str_replace_all(
    oldLevelsReplacement1, mapChinese2
  ) -> oldLevels_translated
}

newLevels <- {
  as.numeric(oldLevels_inArabicNumber) -> arabicNumberLevels
  names(arabicNumberLevels) <- oldLevels
  sort(arabicNumberLevels) -> arabicNumberLevels_sorted
  names(arabicNumberLevels_sorted)
}

# Another possible one
newLevels <- {
  order_index <- order(as.numeric(oldLevels_inArabicNumber))
  oldLevels[order_index]
}

newLevels 
```

c("一", "五","七","拾壹", "參拾參",  "五十七")

```{r}
factor(string, levels= chineseNumberLevel(string))
```

