---
title: "rank chinese number"
output: html_document
---

It is common to rank chinese number 一～十，壹～拾

```{r}
chineseNumber1 <- "零一二三四五六七八九十"
chineseNumber2 <- "零壹貳參肆伍陸柒捌玖拾"
chineseNumber1_char <- unlist(stringr::str_split(chineseNumber1,""))
chineseNumber2_char <- unlist(stringr::str_split(chineseNumber2,""))
```

It would be nice that you can process the following 
```{r}
fct_numbers <- factor(c("一","五","七", "參拾參","五十七","拾壹"))
oldLevels <- levels(fct_numbers)
oldLevels
```
so that its level sequence will be 
```{r}
c("一","五","七","拾壹", "參拾參","五十七")
```
without using
```{r}
levels(fct_numbers) <- c("一","五","七","拾壹", "參拾參","五十七") # OR
fct_numbers <- factor(c("一","五","七", "參拾參","五十七","拾壹"), 
                      levels = c("一","五","七","拾壹", "參拾參","五十七")
)
```

In other words, your algorithm should take these three symbols:

  * `chineseNumber1_char`, `chineseNumber2_char`, `oldLevels`
  

and come out 

  * `newLevels`

which is a character with correct order. (Imagine that oldLevels can be any randomly given string of chinese number characters.)

For simplicity, we assume that `oldLevels` elements are between 0 and 99 in Chinese characters.


```{r}
chineseNumber1 <- "零一二三四五六七八九十"
chineseNumber2 <- "零壹貳參肆伍陸柒捌玖拾"
chineseNumber1_char <- unlist(stringr::str_split(chineseNumber1,""))
chineseNumber2_char <- unlist(stringr::str_split(chineseNumber2,""))
oldLevels <- c("一", "七", "五", "五十七", "參拾參", "拾壹")
```


```{r}
library(stringr)
library(glue)
library(purrr)

# 十位數
tens1 <- map(
  list(3,4,5,6,7,8,9,10),
  ~{paste(chineseNumber1_char[.x], "十", sep = "")}) # 二十、三十、...

tens2 <- map(
  list(3,4,5,6,7,8,9,10),
  ~{paste(chineseNumber2_char[.x], "拾", sep = "")}) # 貳拾、參拾、...

# 個位數

`0` <- map(
  list(1,2,3,4,5,6,7,8,9,10,11),
  ~{c(
    paste(chineseNumber1_char[.x]),
    paste(chineseNumber2_char[.x]))}
)
`0` <- unlist(`0`)
`0` <- `0`[2:22]

{
`11` <- 
  map(
  list(2,3,4,5,6,7,8,9,10),
     ~{c(
       paste("十", chineseNumber1_char[.x], sep = ""),
       paste("拾", chineseNumber2_char[.x], sep = "") )}  )
`11` <- unlist(`11`)
} # 十一、拾壹

{
`21` <- 
  map(
  list(2,3,4,5,6,7,8,9,10),
     ~{c(
       paste(tens1[1], chineseNumber1_char[.x], sep = ""),
       paste(tens2[1], chineseNumber2_char[.x], sep = "") )}  )
`21` <- unlist(`21`)
}

{
`31` <- 
  map(
  list(2,3,4,5,6,7,8,9,10),
     ~{c(
       paste(tens1[2], chineseNumber1_char[.x], sep = ""),
       paste(tens2[2], chineseNumber2_char[.x], sep = "") )}  )
`31` <- unlist(`31`)
}

{
`41` <- 
  map(
  list(2,3,4,5,6,7,8,9,10),
     ~{c(
       paste(tens1[3], chineseNumber1_char[.x], sep = ""),
       paste(tens2[3], chineseNumber2_char[.x], sep = "") )}  )
`41` <- unlist(`41`)
}

{
`51` <- 
  map(
  list(2,3,4,5,6,7,8,9,10),
     ~{c(
       paste(tens1[4], chineseNumber1_char[.x], sep = ""),
       paste(tens2[4], chineseNumber2_char[.x], sep = "") )}  )
`51` <- unlist(`51`)
}

{
`61` <- 
  map(
  list(2,3,4,5,6,7,8,9,10),
     ~{c(
       paste(tens1[5], chineseNumber1_char[.x], sep = ""),
       paste(tens2[5], chineseNumber2_char[.x], sep = "") )}  )
`61` <- unlist(`61`)
}

{
`71` <- 
  map(
  list(2,3,4,5,6,7,8,9,10),
     ~{c(
       paste(tens1[6], chineseNumber1_char[.x], sep = ""),
       paste(tens2[6], chineseNumber2_char[.x], sep = "") )}  )
`71` <- unlist(`71`)
}

{
`81` <- 
  map(
  list(2,3,4,5,6,7,8,9,10),
     ~{c(
       paste(tens1[7], chineseNumber1_char[.x], sep = ""),
       paste(tens2[7], chineseNumber2_char[.x], sep = "") )}  )
`81` <- unlist(`81`)
}

{
`91` <- 
  map(
  list(2,3,4,5,6,7,8,9,10),
     ~{c(
       paste(tens1[8], chineseNumber1_char[.x], sep = ""),
       paste(tens2[8], chineseNumber2_char[.x], sep = "") )}  )
`91` <- unlist(`91`)
}

# 世紀大合併

levels99 <- list(`0`,
                 `11`, tens1[1], tens2[1],
                 `21`, tens1[2], tens2[2],
                 `31`, tens1[3], tens2[3],
                 `41`, tens1[4], tens2[4],
                 `51`, tens1[5], tens2[5],
                 `61`, tens1[6], tens2[6],
                 `71`, tens1[7], tens2[7],
                 `81`, tens1[8], tens2[8],
                 `91`)
levels99 <- unlist(levels99) # 99*2 + "零" = 199

# factor

newLevels <- factor(
  oldLevels,
  levels = levels99
)
```


# 以下失敗過程


```{r}
library(stringr)
library(glue)
library(purrr)

new1 <- oldLevels[str_length(oldLevels)==1] # 一、七、五
new2 <- oldLevels[str_length(oldLevels)==2] # 拾壹
new3 <- oldLevels[str_length(oldLevels)==3] # 五十七、參拾參

new3_1 <- str_subset(new3,pattern = "十") # 五十七
new3_2 <- str_subset(new3,pattern = "拾") # 參拾參

new3_1first <- unlist(str_split(new3_1,"十"))[length(new3_1)/2] # 五
new3_2first <- unlist(str_split(new3_2,"拾"))[1] # 參

factor()

factor(new3,
       levels = 
       )
```

  
```{r}
library(stringr)
library(glue)
library(purrr)



lenth_oldLevel <- map(
  list(1:5),
  ~{length(oldLevels[.x])})

lenth_oldLevel

length(oldLevels[5])

oldLevels[length==3]

pattern_10 <- str_detect(
    oldLevels,
    pattern <- "[十拾]")
  
OverTen <- oldLevels[pattern_10]
LessThanTen <- oldLevels[!pattern_10]

LessThanTen_pattern <- 
unlist(
  map(
  list(1,2,3,4,5,6,7,8,9,10,11),
  ~{c(chineseNumber1_char[.x],chineseNumber2_char[.x])}
))
LessThanTen_pattern[1]<- ""
LessThanTen <- factor(LessThanTen, levels = LessThanTen_pattern)


```
  
  
```{r}
chineseNumber1 <- "零一二三四五六七八九十"
chineseNumber2 <- "零壹貳參肆伍陸柒捌玖拾"
chineseNumber1_char <- unlist(stringr::str_split(chineseNumber1,""))
chineseNumber2_char <- unlist(stringr::str_split(chineseNumber2,""))
oldLevels <- c("一", "七", "五", "五十七", "參拾參", "拾壹")

{ # Your algorithm
  
library(stringr)
library(glue)
library(purrr)

pattern_10 <- str_detect(
    oldLevels,
    pattern <- "[十拾]")
  
TenToNineNine <- oldLevels[pattern_10]
LessThanTen <- oldLevels[!pattern_10]

# 0 ~ 99 排序

units <- map(
  list(1,2,3,4,5,6,7,8,9,10),
     ~{
 
tens <- map(
  list(0,2,3,4,5,6,7,8,9,10,11),
     ~{
       c(
          chineseNumber1_char[.x],
          "十",
          map(
            list(2,3,4,5,6,7,8,9,10),
            ~{c(chineseNumber1_char[.x])})
        )
      }  )

tens <- c()


w <- map(
  list(0,1,2,3,4,5,6,7,8,9),

tens <- map(
  list(0,3,4,5,6,7,8,9,10),
     ~{c(chineseNumber1_char[.x],"十",chineseNumber2_char[.x],"拾")}  )

unlist_tens <- unlist(tens)
pattern_tens <- list()
map(
  list(1:10),
~{pattern_tens[.x] <- paste(unlist_tens[(.x*4-3):(.x*4)],collapse = "")}
)
```





un11 <- unlist(`11`)
pattern11 <- list()

pattern11 <- map(
  list(1:18),
    ~{paste(un11[(2*.x)-1],un11[2*.x])})

z <- map(
  list(0:9),
     ~{
       chineseNumber1_char[.x+1]
      }  )


library(purrr)
test <- map(
c
  ~{
  list(0:9)
      ~{
      .x <- chineseNumber1_char[.x+1]|chineseNumber2_char[.x+1]
      }
    }
  
)

test
  

  
    newLevels <- factor(
    oldLevels,
    levels = c(chineseNumber1_char, chineseNumber2_char[2:10]),
    ordered = TRUE
  )
  
  
}

newLevels 

